Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-27 snapshot_system/fast14_introduction.tex
update

The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
based on  changed block tracking, similarity guided local deduplication,
and popularity guided global deduplication. 
This approach is VM centric by localizing duplicate detection within each VM  
and by packaging only data chunks from the same VM into a file system block as much as possible.
By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
this scheme can afford to allocate extra replicas of these shared chunks for better
fault resilience while sustaining competitive deduplication efficiency.
Localization also brings the benefits of greater ability to exploit parallelism so
backup operations can run simultaneously without a central  bottleneck.
This  VM-centric solution uses  a small amount of  memory while delivering reasonable deduplication efficiency.

>>>>

The key contribution is the development and analysis of a VM-centric approach which integrates  multiple duplicate detection strategies
based on changed block tracking, similarity guided local deduplication,
and popularity guided global deduplication. 
This approach localizes duplicate detection within each VM  
and packages only data chunks from the same VM into a file system block as much as possible.
By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
this scheme can afford to allocate extra replicas of these shared chunks for better
fault resilience while sustaining competitive deduplication efficiency.
In addition, our VM-centric design allows garbage collection to be performed in a localized
scope and we propose an approximate deletion scheme to reduce this cost further.
Localization also brings the benefits of greater ability to exploit parallelism so
backup operations can run simultaneously without a central  bottleneck.
This VM-centric solution uses a small amount of  memory while delivering reasonable deduplication efficiency.
